Lossy compression of DNA sequencing quality data

### 2016-05-06 bmc_manuscript/manuscript.tex
added definitions of additional loss functions

As a measure of compression effectiveness, which reflects the sum of
fixed and marginal costs, we use bits/base-call, defined as the size
of the compressed representation of quality values (in bits) divided
by the number of quality values represented. As a measure of
information loss we use mean squared error (\textsc{mse}) as a loss
function, and define it as $\frac{1}{n}\sum_{i=1}^{n}{(Q_i'-Q_i)^2}$,
where $n$ is the number of quality values, $Q_i'$ is the
compressed/decompressed quality value, and $Q_i$ is the original
quality value associated with position $i$.

>>>>

As a measure of compression effectiveness, which reflects the sum of
fixed and marginal costs, we use bits/base-call, defined as the size
of the compressed representation of quality values (in bits) divided
by the number of quality values represented. As measures of
information loss we use three loss functions: mean squared error
(\textsc{mse}), defined as $\frac{1}{n}\sum_{i=1}^{n}{(Q_i'-Q_i)^2}$;
mean absolute deviation (\textsc{mad}), defined as
$\frac{1}{n}\sum_{i=1}^{n}{|Q_i'-Q_i|}$; and mean Lorentz distortion,
defined as $\frac{1}{n}\sum_{i=1}^{n}{log_{2}(1 + |Q_i'-Q_i|)}$, where
$n$ is the number of quality values, $Q_i'$ is the
compressed/decompressed quality value, and $Q_i$ is the original
quality value associated with position $i$.
